---  
title: "Logic of RSiena"
bibliography: references.bib
link-citations: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"), cache.lazy = FALSE)
options(width = 100) 
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE, message=FALSE}
# install.packages("remotes")
#remotes::install_github("rlesur/klippy")
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

------------------------------------------------------------------------

# Introduction

```{=html}
<script>
function myFunction() {

            var btn = document.getElementById("myButton");
            //to make it fancier
            if (btn.value == "Click to hide code") {
                btn.value = "Read more";
                btn.innerHTML = "Read more";
            }
            else {
                btn.value = "Click to hide code";
                btn.innerHTML = "Read less";
            }
            //this is what you're looking for
            var x = document.getElementById("myDIV");
            if (x.style.display === "none") {
                x.style.display = "block";
            } else {
                x.style.display = "none";
            }
        }
          
</script>
```
Welcome to the website of the Sunbelt 2024 Workshop: **RSiena**

<br>

TEXT HERE

<!--

<button class="button1" onclick="myFunction()" id="myButton" value="Click To Open Instructions">

Read more

</button>

::: {#myDIV style="display:none;"}
<br>

more text here

<br>
:::

--->

------------------------------------------------------------------------

# Getting started

## LabJournal

During the course, students will journal their work and assignments in
their custom lab journal. A template lab journal can be found on
[GitHub](https://github.com/robfranken/LabJournal). Here, you find how
to get started.


------------------------------------------------------------------------

# Program

The program of this workshop will be as follows:

`r colorize("Introduction", "red")`\
*Time: 9:00am - 9:30am*:    
    - round of introductions  
    - Our GOALS for today

`r colorize("Lab Journal", "red")`\
*Time: 9:30am - 10:00am*:  
    -   [Lab Journal](https://github.com/robfranken/LabJournal)

`r colorize("Logic of RSiena", "red")`\
*Time: 10:00am - 11:30am*

`r colorize("BREAK", "red")`\
*Time: 11:30am - 11:45am*

`r colorize("Constructing RSiena data objects", "red")`\
*Time: 11:45am - 12:30pm*

`r colorize("BREAK", "red")`\
*Time: 12:30pm - 1:45pm*

`r colorize("Yes finally using RSiena to estimate a model", "red")`\
*Time: 1:45pm - 2:30pm*

`r colorize("RSiena GOF", "red")`\
*Time: 2:30pm - 3:30pm*

`r colorize("Let's practice", "red")`\
*Time: 3:30pm - 4:30pm*

---  

